Breeding bird indicators

### 2023-10-23 trophic_levels-biomass_indicators.rmd

```{r, message=FALSE, warning=FALSE}
#| label: Data-import
#| cache: TRUE

@@

```{r, message=FALSE, warning=FALSE, fig.cap= "Net primary production over Norway"}
#| label: Plotting-basic-data
#| cache: TRUE

@@

```{r, message=FALSE, warning=FALSE}
#| label: PlotTotalHerbivoreBiomass
#| cache: TRUE
#| fig.cap: "Herbivore biomass over Norway"

@@

```{r, message=FALSE, warning=FALSE}
#| label: Plot-carnivore-biomass
#| cache: TRUE
#| fig.cap: "Carnivore biomass over Norway"
carnivorerast<-rast(paste0(pData,"/Trophic_levels/Carnivores_RawBiomass.tiff"))

@@

```{r, message=FALSE, warning=FALSE}
#| label: Calculating-expected-herbivore-biomass
#| cache: TRUE
#| fig.cap: "Expected herbivore biomass"
expected_herbivore_biomass<-(npprast_yrs^0.47 * 0.643)#Global 
ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
  ggtitle("Expected herbivore biomass")+
  geom_spatraster(data=expected_herbivore_biomass)+facet_wrap(~lyr)+theme_bw()+
  scale_fill_continuous(low='lightskyblue',high="darkblue",na.value=NA,expression('kg km'^-2))

@@

```{r}
#| label: DifferenceHerbivoreBiomass
#| cache: TRUE
#| fig.cap: "Difference from expected herbivore biomass"
totalherbivorebiomass<-livestockrast[[sapply(strsplit(names(livestockrast),"_"),'[',1) %in% "TotalHerbivoreBiomass"]]
names(totalherbivorebiomass)<-allyears_vect
totalherbivorebiomass_npp<-totalherbivorebiomass[[names(totalherbivorebiomass) %in% c("1999","2009","2015")]]

@@

```{r}
#| label: Expected-carnivore-biomass
#| cache: TRUE 
#| fig.cap: "Expected carnivore biomass"
#| warning: FALSE

@@

```{r diff-carnivores-tlb, fig.cap="Difference from expected carnivore biomass"}
diffcarn<-100* (totalcarnivores-expected_carnivore_biomass)/(expected_carnivore_biomass+1)
names(diffcarn)<-allyears_vect

>>>>

```{r, message=FALSE, warning=FALSE}
#| label: data-import

@@

```{r, message=FALSE, warning=FALSE, fig.cap= "Net primary production over Norway"}
#| label: Plotting-basic-data

@@

```{r, message=FALSE, warning=FALSE}
#| label: PlotTotalHerbivoreBiomass
#| fig.cap: "Herbivore biomass over Norway"

@@

```{r, message=FALSE, warning=FALSE}
#| label: Plot-carnivore-biomass
#| fig.cap: "Carnivore biomass over Norway"
carnivorerast<-rast(paste0(pData,"/Trophic_levels/Carnivores_RawBiomass.tiff"))

@@

```{r, message=FALSE, warning=FALSE}
#| label: Calculating-expected-herbivore-biomass
#| fig.cap: "Expected herbivore biomass"
expected_herbivore_biomass<-(npprast_yrs^0.47 * 0.643)#Global 
ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
  ggtitle("Expected herbivore biomass")+
  geom_spatraster(data=expected_herbivore_biomass)+facet_wrap(~lyr)+theme_bw()+
  scale_fill_continuous(low='lightskyblue',high="darkblue",na.value=NA,expression('kg km'^-2))

@@

```{r}
#| label: DifferenceHerbivoreBiomass
#| fig.cap: "Difference from expected herbivore biomass"
totalherbivorebiomass<-livestockrast[[sapply(strsplit(names(livestockrast),"_"),'[',1) %in% "TotalHerbivoreBiomass"]]
names(totalherbivorebiomass)<-allyears_vect
totalherbivorebiomass_npp<-totalherbivorebiomass[[names(totalherbivorebiomass) %in% c("1999","2009","2015")]]

@@

```{r}
#| label: Expected-carnivore-biomass
#| fig.cap: "Expected carnivore biomass"
#| warning: FALSE

@@

```{r diff-carnivores-tlb, fig.cap="Difference from expected carnivore biomass"}
diffcarn <-100*(totalcarnivores-expected_carnivore_biomass)/(expected_carnivore_biomass+1)
names(diffcarn) <- allyears_vect
